04-plot characteristics

### 2018-05-28 02_scripts/04_plot_characteristics.Rmd
28/05/2018

@@

```{r}
df <- tibble(
  plot = factor(c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun")),
  rmse = c(89.89, 30.37, 76.02, 106.65),
  point_dens = c(34.34, 62.51, 33.76, 35.01),
  mean_defol = c(53.22, 17.73, 68.35, 44.63)
)
```

@@

## RMSE vs mean defol

```{r}
rmse_defol <- ggplot(df, aes(x = mean_defol, y = rmse)) +
  geom_point(aes(color = plot), shape = 19, size = 3) +
  labs(x = "Mean defoliation (%)", y = "RMSE") +
  theme_ipsum_rc(
    axis_title_size = 22,
    axis_title_just = "c"
  ) +
  scale_color_nejm() +
  theme(
    plot.margin = unit(c(6, 0, 6, 0), "pt"),
    legend.position = "none",
    axis.text = element_text(size = 20),
    legend.text = element_text(size = 20),
    axis.title.y = element_text(margin = margin(
      t = 0, r = 15,
      b = 0, l = 0
    )),
    axis.title.x = element_text(margin = margin(
      t = 15, r = 0,
      b = 0, l = 0
    ))
  )
```

>>>>

# Coefficient of variation

```{r}
data %>%
  group_by(plot) %>%
  summarise((sd(deftot) / mean(deftot)) * 100)
```

#  sd / skewness

```{r}
data %>%
  group_by(plot) %>%
  summarise(((sd(deftot) / mean(deftot)) * 100) / skewness(deftot))
```

```{r}
data %>%
  group_by(plot) %>%
  summarise(sd(deftot))
```

@@

```{r}
df <- tibble(
  plot = factor(c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun")),
  rmse = c(89.89, 30.37, 76.02, 106.65),
  point_dens = c(34.34, 62.51, 33.76, 35.01),
  mean_defol = c(53.22, 17.73, 68.35, 44.63),
  cov_defol = c(44.88707	, 115.78180	, 12.17709	, 83.18840),
  sd_skewness = c(-55.077546, 67.232146, -3.187733	, -401.564010)
)
```

@@

## RMSE vs coef of variation

```{r}
rmse_defol <- ggplot(df, aes(x = sd_skewness, y = rmse)) +
  geom_point(aes(color = plot), shape = 19, size = 3) +
  labs(x = "Coefficient of variation (%) / Skewness", y = "RMSE") +
  theme_ipsum_rc(
    axis_title_size = 22,
    axis_title_just = "c"
  ) +
  scale_color_nejm() +
  theme(
    plot.margin = unit(c(6, 0, 6, 0), "pt"),
    legend.position = "none",
    axis.text = element_text(size = 20),
    legend.text = element_text(size = 20),
    axis.title.y = element_text(margin = margin(
      t = 0, r = 15,
      b = 0, l = 0
    )),
    axis.title.x = element_text(margin = margin(
      t = 15, r = 0,
      b = 0, l = 0
    ))
  )
```
